### 2017-05-30 paper.tex
Fix starting sentence with however
little to small for clearer meaning

Thinking systematically about difficulty levels can help manage expectations.
For example,
the Programming Historian project labels lessons ``beginner''",
``intermediate'',
and ``advanced''
to help authors write at appropriate levels.
However,
this only works if there is prior agreement on what those terms mean.

@@

\item
  This workshop will show Jorge how to write a little Python program
  to read the data,
  select the right values from each file,
  and calculate the required statistics.

>>>>

Thinking systematically about difficulty levels can help manage expectations.
For example,
the Programming Historian project labels lessons ``beginner''",
``intermediate'',
and ``advanced''
to help authors write at appropriate levels.
This method works, however, only if there is prior agreement on what those terms mean.

@@

\item
  This workshop will show Jorge how to write a small Python program
  to read the data,
  select the right values from each file,
  and calculate the required statistics.
